A boundary-integral framework to simulate \\ viscous erosion of a porous medium

### 2018-04-10 docs/methods/erosion_methods.tex
NM

Recent work in the high-Reynolds-number regime has highlighted the importance of a shape-flow feedback that occurs during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann} and the related processes of dissolution and melting~\cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.  In these cases, the flow alters the morphology of the immersed structures, which in turn modifies the surrounding flow, and so on. Such processes of `sculpting with flow' \cite{ristroph2018sculpting} have been examined in the context of a single body \cite{ris-moo-chi-she-zha2012} and, more recently, multiple bodies whose shape evolution is coupled through the flow \cite{hewett2017evolution, moore2017riemann}.
From this viewpoint, the example of an eroding porous medium presents new opportunities and challenges. First, since the medium is composed of many individual constituents, multi-body interactions must be considered. Second, the long-range effects inherent to Stokes flow implies that the shape-evolution of bodies are even more strongly coupled than in any other regime.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions\label{s:conclusions}}
We have combined two accurate and stable numerical methods to simulate two-dimensional viscous erosion in a porous medium.  First, a BIE formulation of the incompressible Stokes equations discretizes only the boundary of the bodies and resolves their non-negligible interactions.  Second, the bodies are evolved with the so-called {\thL} variables to avoid tangling and distortion of the mesh.  The resulting numerical method is spectral in space, second-order in time, and is accelerated with the fast multipole method.

Using slender body theory and flow past a wedge, the method is verified against analytical results for the area, opening angle, and total drag of a single eroding body.  Then, for multi-body erosion with a realistic pressure drop boundary condition, we compute the area fraction, flow rate, and total drag across a channel.  We observe that erosion leads to channelization, and this reduces the resistance more than would be expected if the area fraction were reduced by simply scaling down the size of the bodies.  This indicates that the area fraction can not fully characterize flow in eroding porous media since the interactions between the bodies plays a role in the resistance.

>>>>

Recent work in the high-Reynolds-number regime has highlighted the importance of a shape-flow feedback that occurs during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann} and the related processes of dissolution and melting~\cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.  In these cases, the flow alters the morphology of the immersed structures, which in turn modifies the surrounding flow, and so on. Such processes of `sculpting with flow' \cite{ristroph2018sculpting} have been examined in the context of a single body \cite{ris-moo-chi-she-zha2012} and, more recently, multiple bodies whose shape evolution is coupled through the flow \cite{hewett2017evolution, moore2017riemann}.
From this viewpoint, the example of an eroding porous medium presents new opportunities and challenges. First, since the medium is composed of many individual constituents, multi-body interactions must be considered. Second, the long-range effects inherent to Stokes flow implies that the shape-evolution of bodies are even more strongly coupled than in any other regime.
% in particular close-contacts?

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions\label{s:conclusions}}

We have combined two accurate and stable numerical methods to simulate two-dimensional viscous erosion in a porous medium.  First, a BIE formulation of the incompressible Stokes equations discretizes only the boundary of the bodies and resolves their non-negligible interactions.  Second, the bodies are evolved with the so-called {\thL} variables to avoid tangling and distortion of the mesh.  The resulting numerical method is spectral in space, second-order in time, and is accelerated with the fast multipole method.

%Using slender body theory and flow past a wedge, the method is verified against analytical results for the area, opening angle, and total drag of a single eroding body.  Then, for multi-body erosion with a realistic pressure drop boundary condition, we compute the area fraction, flow rate, and total drag across a channel.  We observe that erosion leads to channelization, and this reduces the resistance more than would be expected if the area fraction were reduced by simply scaling down the size of the bodies.  This indicates that the area fraction can not fully characterize flow in eroding porous media since the interactions between the bodies plays a role in the resistance.
